Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-23 papers/ignition/paper.tex
Add caveats about the implications

This story contains two important lessons. First, the required resolution for even a qualitatively converged
simulation, less than 100 m, is out of reach of current 3D supernova simulations. Second, the behavior for
resolutions worse than 1 km qualitatively appears to be converged, and one could perhaps be misled into
thinking that there was no reason to try higher resolutions, which is reason for caution in interpreting
reacting hydrodynamics simulations.

@@

Our example detonation problem demonstrates, at least for this class of
hydrodynamical burning problem, a grid resolution requirement much more stringent
than 1 km. This test does not, of course, represent all possible WD burning conditions.
However, the fact that it is even possible for burning in white dwarf material to require a
resolution better than 100 m should cast significant uncertainty on the results
of simulations featuring detonations that do not meet this resolution,
regardless of the specific conditions. Or, at least, it should suggest
that stronger demonstrations of convergence are required, especially bearing in mind
our observation that the numerical instability can result in simulations that
appear qualitatively converged when the resolution is increased by a factor of
one or two orders of magnitude but not three orders of magnitude.

>>>>

This story contains two important lessons. First, the required resolution for even a qualitatively converged
simulation, less than 100 m, is out of reach \replaced{of current 3D supernova simulations}{for an analogous
simulation done in 3D}. Second, the behavior for 
resolutions worse than 1 km qualitatively appears to be converged, and one could perhaps be misled into
thinking that there was no reason to try higher resolutions, which is reason for caution in interpreting
reacting hydrodynamics simulations. \added{With that being said, our 1D tests are not directly comparable to
previous multi-dimensional WD collision simulations. The 1D tests should not be substituted for understanding the
actual convergence properties of the 2D/3D simulations, which may have different resolution requirements for
convergence. Our tests suggest only that it is plausible that simulations at kilometer-scale (or worse) resolution
are unconverged. This observation is, though, consistent with the situation described in \autoref{sec:introduction},
where our 2D WD collision simulations (not shown here) are unconverged, and many of the previous collision simulations
presented in the literature have relatively weak evidence for convergence.}

@@

Our example detonation problem demonstrates, at least for this class of
hydrodynamical burning problem, a grid resolution requirement much more stringent
than 1 km. This test does not, of course, represent all possible WD burning conditions.
However, the fact that it is even possible for burning in white dwarf material to require a
resolution better than 100 m should \deleted{cast significant uncertainty on the results
of simulations featuring detonations that do not meet this resolution,
regardless of the specific conditions. Or, at least, it should} suggest
that stronger demonstrations of convergence are required \added{for simulations that
do not meet this resolution}. \replaced{especially} {This is especially true} bearing in mind
our observation that the numerical instability can result in simulations that
appear qualitatively converged when the resolution is increased by a factor of
one or two orders of magnitude but not three orders of magnitude.
